Peaks Over Threshold for Bursty Time Series

### 2018-04-16 article_springer/article_springer.Rmd
simplified proof

>>>>

_Proof of Theorem:_
We interpret the threshold crossing time as the hitting time of the 
underlying CTRM (Continuous Time Random Maxima) or "max-renewal process", 
and then utilize a result by @MeerschaertStoev08. 
The running maximum process is defined as 
$$
M_J(c) := J_1 \vee \ldots \vee J_{\lfloor c \rfloor},
$$
and since we assume that the $J_k$ have a continuous distribution, there exist 
norming functions $a(c)$ and $d(c)$ such that 
$$
\mathbf P\left[ \frac{M_J(c) - d(c)}{a(c)} \le \ell^* \right] 
\stackrel{d}{\longrightarrow} F(\ell^*), \quad t \to \infty
$$
where $F$ is a generalized extreme value distribution, and $\ell^*$ is any 
value from the support of $F$.

The underlying CTRM is then defined via 
$$
M(t) = M_J(N(t)), \quad t \ge 0
$$
where $N(t)$ is the renewal process associated with the waiting times 
$W_k$: 
$$
N(t) = \max\{n: W_1 + \ldots + W_n \le t\}.
$$
Now a key observation is that
$$
T(\ell) = \inf\{t: V(t) > \ell\}, 
$$
and that 
$$
T(\ell) > t \quad \text{ if and only if } \quad V(t) \le \ell.
$$
By [Theorem 3.1, @MeerschaertStoev08], we have the stochastic process 
convergence 
$$
\frac{M(ct) - d(\tilde b(c))}{a(\tilde b(c))} \stackrel{d}{\longrightarrow} 
M(t), \quad t > 0.
$$
where $M(t)$ is a time-changed ("subordinated") extremal process, and where 
$\tilde b(c)$ is a regularly varying norming function which is
_inverse_ to $b(c)$, in the sense that 
$b(\tilde b(c)) \sim c \sim \tilde b(b(c))$.

Without loss of generality, we choose $\ell^*$ such that $F(\ell^*) = 1/e$, 
and let $\ell = a(\tilde b(c)) \ell^* + d(\tilde b(c))$. 
We may then calculate 
$$
\mathbf P\left[ \frac{T(\ell)}{b(1/p)} > t \right]
= \mathbf P[T(\ell) > b(1/p) t]
= \mathbf P[M(ct) \le \ell]
= \ldots
$$
where we have substituted $c = b(1/p)$, 
$$
\ldots
= \mathbf P\left[ \frac{M(ct) - d(\tilde b(c))}{a(\tilde b(c))} 
\le \frac{\ell - d(\tilde b(c))}{a(\tilde b(c))} \right]
\longrightarrow \mathbf P\left[ M(t) \le \ell^* \right]
= \ldots
$$
Defining the hitting time of level $\ell^*$ by $M(t)$ as 
$$
\xi_{\ell^*} := \inf\{t: M(t) > \ell^*\}
$$
we then have 
$$
\ldots = \mathbf P[\xi_{\ell^*} > t] 
= \mathbf P[(-\log F(\ell^*))^{-1/\beta} X^{1/\beta} D]
$$
by [Proposition 4.2, @MeerschaertStoev08]. Using [Theorem 19.1, @Haubold11], 
we see that $X^{1/\beta} D \sim {\rm ML}(\beta, 1)$, concluding the proof.

# Statistics of the Mittag-Leffler distribution
